---
title: "College Graduation Correlation"
author: "Josh Sutton"
date: "2024-02-11"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(magrittr)  
library(ggplot2)   # ploting graphs library
library(cowplot)   # Graph Aesthetic

library(wordcloud) # wordcloud graph
knitr::opts_chunk$set(echo = TRUE)
```

## College Selected Info Table
```{r}
unis <- read.csv("College_Data.csv") %>% 
  select(X,Private, Accept, Enroll, Top10perc,Grad.Rate) %>% 
  rename(College = X) %>% 
  arrange(Grad.Rate)
head(unis,15)
```

\newpage

## College Modified Info Table with Tibble
```{r}
unisMod <- read.csv("College_Data.csv")  %>%
  mutate(Enroll.Rate = (Enroll / Accept)*100) %>% 
  mutate(Accept.Rate = (Accept / Apps)*100) %>% 
  select(X, Private, Apps, Accept.Rate,Enroll, Enroll.Rate, Grad.Rate)
as_tibble(unisMod)
```

\newpage

# Visualizing College Data as Scatter Plot
```{r}
unisMod %>% ggplot(aes(Enroll.Rate,Grad.Rate,color = Private)) + geom_point(size=2) +
  scale_color_manual(labels = c("Private", "Public"), 
                     values = c("deepskyblue", "brown1")) +
  labs(
    title = "Enrollment vs. Graduation Rates of private and public colleges",
    x = "Enrollment Rate",
    y = "Graduation Rate",
    color = "College Type"
  ) + theme_minimal_grid(12)
```

|    This visualization coming from Lab Journal 3 is a scatter plot of private and public colleges and the comparison between enrollment rates and graduation rates of each college. From this graph we can see public colleges tend to have a lower enrollment rate but a higher graduation rate while private colleges tend to have a slightly higher enrollment rate and lower graduation rate. 

\newpage

# Visualizing using a Bubble Chart
```{r}
unisMod %>% filter(Private=='No') %>% filter(Enroll >=600) %>% 
  ggplot(aes(x = Accept.Rate, y = Grad.Rate, size = Enroll.Rate)) +
  geom_point(alpha = 0.5, color = "blue", fill = "black", shape = 21) +
  labs(
    title = "Grad. Rates of large incoming Public Colleges comparing Accept to Enroll rates",
    x = "Acceptance Rate",
    y = "Enrollment Rate",
    size = "Graduation Rate"
  ) + scale_size(range = c(1,20))
```

|    This bubble chart coming from Lab Journal 3 is a 2D visualization of public colleges who enrolled 600 or more students. Point location is based on comparison between acceptance rate and enrollment rates. Each point size is determined by graduation rate. We can see that most colleges are found with a 70-90% acceptance rate and a 50% enrollment rate and roughly the colleges found in this area tend to have a graduation rate of 60% or less.

\newpage
# Word Cloud
```{r}
#png("wordcloud.png",width=20,height=8,units="in",res=300)
par(mar = rep(0,4))
set.seed(458)
unisHighAccept <- unisMod %>% filter(Grad.Rate > 90)
wordcloud(words = unisHighAccept$X, freq = unisHighAccept$Enroll, scale= c(1.7,0.25),
                             max.words = 91, colors = brewer.pal(8,"Dark2"))
```

|    Visualization coming from Lab Journal 3, word clouds are used to display frequency of words through visualization where bigger words tie to more frequent appearance. This word cloud displays all colleges with a 90% graduation rate or higher and the frequency is the total amount of students enrolled in 2019. With more and more data the more difficult it becomes to see differences in words and more difficult to find desired words.

